Using traffic analysis to identify The Second Generation Onion Router

### 2011-04-17 thesis/results.tex
Put conclusion and results back into their own chapter.
Add description of ROC area statistic in results table

@@

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    & True Positive Rate & False Positive Rate & ROC \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Random Tree\\
    \midrule
    HTTPS & 0.961 & 0.046 & 0.963\\
    HTTP over Tor & 0.906 & 0.04 & 0.94\\
    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
    Weighted Avg. & 0.941 & 0.037 & 0.957\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

>>>>

\chapter{Results}

@@

The table includes the true positive and false positive rate rate of each algorithm and
include the area under the receiver operating characteristic (ROC) curve. The
ROC is a tool used for evaluating the usefulness and comparing different
matching algorithms and is often used to compare Internet traffic
classification techniques \parencite{citeulike:167557,Nguyen:2008p3837}.

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    & True Positive Rate & False Positive Rate & ROC Area \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Random Tree\\
    \midrule
    HTTPS & 0.961 & 0.046 & 0.963\\
    HTTP over Tor & 0.906 & 0.04 & 0.94\\
    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
    Weighted Avg. & 0.941 & 0.037 & 0.957\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

\chapter{Conclusion}
